A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Finish Symbolic model checking
Add Alternative representations intro

\tbr

@@

\tbd

>>>>

Utilizing these equivalent representations, one efficient CTL model checking.
Moreover, Burch, Clarke, McMillan and Dill~\cite{BURCH90-2} described how to use
these methods to do \textit{fair} CTL model checking. \tbr

@@

In this last section, some alternative representations of BDDs are discussed
briefly, e.g. BMDs or BEDs. These representations were introduced primarily
because the OBDD representation is insufficient for some problems of practical
relevance. Bryant~\cite{BRYANT95} already reviewed most alternative represenations
but some were introduced after this overview, e.g. the
\textit{Binary Expression Diagrams} introduced by Andersen and
Hulgaard~\cite{ANDERSEN97}. \tbr
